---
title: "Docket Analytics and Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Docket Analytics and Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)
```


This page provides preliminary data analytics on various advanced reactor dockets. 
Note that ADAMS assigned multiple docket numbers to some reports.
The results presented here should be interpreted with these limitations.

This page is updated Monday through Friday, hourly between 9AM ET and 5 PM ET. 
The last update was at `r Sys.time() |> lubridate::ymd_hms() |> lubridate::with_tz("America/New_York")` ET.

# Pulling Advanced Reactor Docket Files


```{r}
combined_dockets <- nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(rest_api = TRUE) |>
  nrcadams::hyperlink_file_to_name() |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::select(-c(Company, DocketNumber, `ML Number`)) |>
  dplyr::filter(!is.na(Project)) |>
  dplyr::mutate(Project = stringr::str_replace(Project, "Application", "App."))

docket_count <- combined_dockets |>
  dplyr::count(Project, sort = TRUE)

docket_count |>
  DT::datatable()
```

# Docket Plots

## Bar Plots

There are too many document types coded by ADAMS to effectively show on a plot 
(i.e., > 180).
As a result, the Type field is binned to facilitate a bar plot of various 
reactor applications. 

```{r, fig.height = 7}
library(ggplot2)
docket_types = combined_dockets |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
  ) |>
  nrcadams::simplify_type()

type_count = docket_types |>
  dplyr::filter(NLWR) |>
  dplyr::count(Type, sort = TRUE) |>
  dplyr::arrange(n)


plt = docket_types |>
  dplyr::mutate(Type = factor(Type, levels = type_count |> dplyr::pull(Type))) |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type)) +
    theme_bw() +
    scale_fill_brewer(palette="Set1") +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    xlab("Document Count")

plt |> plotly::ggplotly(tooltip = c("Type", "count"))
```

The same data can also be plotted with the bars unstacked.

```{r, fig.height = 7}
plt = docket_types |>
  dplyr::mutate(Type = factor(Type, levels = type_count |> dplyr::pull(Type))) |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type), position = position_dodge()) +
    theme_bw() +
    scale_fill_brewer(palette="Set1") +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    xlab("Document Count")

plt |> plotly::ggplotly(tooltip = c("Type", "count"))
```

## Time Series


The plot below shows the number of documents submitted to a docket. 
Plot order is sorted from highest number of documents, `r docket_count |> dplyr::filter(n == max(n)) |> dplyr::pull(Project)` 
to lowest number of documents, `r docket_count |> dplyr::filter(n == min(n)) |> dplyr::pull(Project)`.

### Cumulative Plots

The cumulative number of documents on a given ADAMS docket is also presented
as a function of document date. 
Due to the large number of plots, **it is suggested that you use the interactive 
plot filter function.** 
By clicking on a project name in the legend, you can remove that project from
the plot to better focus on the remaining projects.


```{r}
plot_min_date = "2020-01-01" |> lubridate::ymd()

grouped_dockets = combined_dockets |>
  dplyr::group_by(Project) |>
  dplyr::arrange(`Publish Date`) |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
    count = 1,
    `Document Count` = cumsum(count),
    `Publish Date` = `Publish Date` |> lubridate::as_date()
    ) 

plt = grouped_dockets |>
  dplyr::filter(`Publish Date` > plot_min_date) |>
  ggplot() +
    geom_step(aes(x = `Publish Date`, y = `Document Count`, color = Project)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    scale_y_continuous(
      breaks= seq(
        0, 
        max(grouped_dockets$`Document Count`), 
        by = 200
        )
      ) +
    scale_x_continuous(
      breaks= seq(
        min(plot_min_date), 
        max(grouped_dockets$`Publish Date` |> lubridate::as_date()) , 
        by = "quarter"
        )
      )
```

The data in linear scale:

```{r, fig.height = 9, fig.width = 9}
plt |> plotly::ggplotly()
```
The data in a y axis semi log scale:

```{r, fig.height = 9, fig.width = 9}
plt = plt + scale_y_log10() 
plt |> plotly::ggplotly()
```

### Cumulative Plots (By Document Type)

**This section is a work in progress**

Dockets can often be cluttered by affidavits, meeting notices, and other documents that can obscure insights. 
Reclassifying these documents using the `simplify_type` function and then removing the `Other` type can help
see what is really going on in a docket. 
**Warning, in order to see what is happening in each docket, the y-axis is allowed to rescale to each docket. This can make comparing dockets difficult.**

```{r, fig.height = 25, fig.width = 9}

grouped_project_type <-  combined_dockets |>
  nrcadams::simplify_type() |>
  dplyr::filter(!Type == "Other") |>
  dplyr::group_by(Project, Type) |>
  dplyr::arrange(`Publish Date`) |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
    count = 1,
    `Document Count` = cumsum(count),
    `Publish Date` = `Publish Date` |> lubridate::as_date()
    ) 

plt <- grouped_project_type |>  
  dplyr::filter(lubridate::as_date(`Publish Date`) > plot_min_date) |>
  ggplot() +
    geom_step(aes(x = `Publish Date`, y = `Document Count`, color = Type)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    scale_x_continuous(
      breaks= seq(
        min(plot_min_date), 
        max(grouped_project_type$`Publish Date` |> lubridate::as_date()) , 
        by = "quarter"
        )
      ) +
    facet_grid(vars(Project), scales = "free_y")

plt |> plotly::ggplotly()
```


### Smoothed Interaction Rates

The daily document rate provides a metric to gauge the level of interactions
between a project and the NRC at a given point in time. 
Unlikely the cumulative plots, this metric is memory-less and thus is not 
impacted by prior interactions.
Due to the large number of plots, **it is suggested that you use the interactive
plot filter function.**
By clicking on a project name in the legend, you can remove that project from
the plot to better focus on the remaining projects.

```{r, fig.height = 12}
smoothed_grouped_dockets = combined_dockets |>
  dplyr::arrange(`Publish Date`) |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
    count = 1,
    `Day Published` = paste(
      `Publish Date` |> lubridate::year(), 
      `Publish Date` |> lubridate::month(), 
      `Publish Date` |> lubridate::day(),
      sep = '/'
      ) |> lubridate::ymd()
    ) |>
  dplyr::group_by(`Day Published`, Project) |>
  dplyr::summarise(`Daily Document Count` = sum(count)) |>
  dplyr::group_by(Project) |>
  tidyr::complete(
    `Day Published` = seq.Date(
      min(`Day Published`), 
      max(`Day Published`), 
      by = "day"
      ),
    fill = list(`Daily Document Count` = 0)
    ) |>
  dplyr::mutate(
    `Smoothed Daily Document Rate` = zoo::rollmean(
      `Daily Document Count`, k = 30, na.pad = TRUE, align = "center"
      )
    ) 

plt = smoothed_grouped_dockets |>
  dplyr::filter(`Day Published` > plot_min_date) |>
  ggplot() +
    geom_step(
      aes(x = `Day Published`, y = `Smoothed Daily Document Rate`, color = Project)
    ) +
    theme_bw() +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
  scale_y_continuous(
    breaks= seq(
      0, 
      max(smoothed_grouped_dockets$`Smoothed Daily Document Rate`, na.rm = TRUE), 
      by=1
      )
    ) +
  scale_x_date(
    breaks= seq(
      plot_min_date, 
      max(smoothed_grouped_dockets$`Day Published`), 
      by = "year")
    )

plt |> plotly::ggplotly()
```

Unfortunately, the data in this plot is a bit clustered so it is hard to 
pinpoint the trend of any given docket. 
Facet plots can separate out any given docket to more easily decipher trends. 

```{r, fig.height = 25}
facet_dockets =  smoothed_grouped_dockets |>
  dplyr::mutate(
    Project = dplyr::case_when(
      Project |> stringr::str_detect("Part 50") ~ Project |> stringr::str_replace(" Part 50", ""),
      Project |> stringr::str_detect("Part 52") ~ Project |> stringr::str_replace(" Part 52", ""),
      Project |> stringr::str_detect("Part 70") ~ Project |> stringr::str_replace(" Part 70", ""),
      TRUE ~ Project |> stringr::str_replace(" Pre-App.", "")
      )
    ) |>
  tidyr::pivot_longer(
    c(`Daily Document Count`, `Smoothed Daily Document Rate`), 
    names_to = "Plot Type",
    values_to = "count"
    ) |>
  dplyr::mutate(
    `Plot Type` = dplyr::case_when(
      `Plot Type` == "Daily Document Count" ~ "Raw Counts",
      TRUE ~ "Smoothed"
    ),
    count = count |> signif(1)
  )

plt = facet_dockets |>  
  dplyr::filter(`Day Published` > plot_min_date) |>
  ggplot() +
    geom_step(
      aes(x = `Day Published`, y = count, color = `Plot Type`)
    ) +
    theme_bw() +
    theme(legend.position="top") +
    labs(
      title = "Advanced Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
  scale_y_continuous(
    breaks= seq(
      0, 
      6, 
      by=1
      ),
    limits = c(0,5.5)
    ) +
  scale_x_date(
    breaks= seq(
      plot_min_date, 
      max(facet_dockets$`Day Published`), 
      by = "year")
    ) +
  facet_grid(vars(Project)) +
  ylab("Daily Document Count")

plt |> plotly::ggplotly()
```

## Docket Statistics

With the basic docket information parsed in previous sections, basic 
summary statistics can be computed to compare the state of various dockets 
at a glance.

```{r}
seconds_per_year = 365 * 24 *60 *60
smoothed_grouped_dockets |>
  dplyr::group_by(Project) |>
  dplyr::summarise(
    `First Date` = min(`Day Published`[`Daily Document Count` > 0]),
    `Last Date` = max(`Day Published`[`Daily Document Count` > 0]),
    `Total` = sum(`Daily Document Count`),
    `Years` = round(lubridate::interval(`First Date`, `Last Date`) |> lubridate::int_length() / seconds_per_year, digits = 2),
    `Yearly Rate` = round(Total / Years, digits = 2)
    ) |>
  DT::datatable()
```

<!-- ### Monthly Rates -->

<!-- The monthly document rate provides a metric to gauge the level of interactions -->
<!-- between a project and the NRC at a given point in time that is memory-less -->
<!-- (i.e., not impacted by prior interactions).  -->
<!-- Due to the large number of plots, **it is suggested that you use the interactive  -->
<!-- plot filter function.**  -->
<!-- By clicking on a project name in the legend, you can remove that project from -->
<!-- the plot to better focus on the remaining projects. -->

<!-- ```{r, fig.height = 7} -->
<!-- grouped_dockets = combined_dockets |> -->
<!--   dplyr::arrange(`Publish Date`) |> -->
<!--   dplyr::mutate( -->
<!--     Project = factor(Project, levels = docket_count |> dplyr::pull(Project)), -->
<!--     count = 1, -->
<!--     `Month Published` = paste( -->
<!--       `Publish Date` |> lubridate::year(),  -->
<!--       `Publish Date` |> lubridate::month(),  -->
<!--       sep = '/' -->
<!--       ) |> lubridate::ym() -->
<!--     ) |> -->
<!--   tidyr::complete(Project, `Month Published` = seq(min(`Month Published`), max(`Month Published`), by = "month")) |> -->
<!--   dplyr::group_by(`Month Published`, Project) |> -->
<!--   dplyr::summarise(`Monthly Document Count` = sum(count)) |> -->
<!--   dplyr::mutate(`Monthly Document Count` = tidyr::replace_na(`Monthly Document Count`, 0.1)) |> -->
<!--   dplyr::ungroup() |> -->
<!--   dplyr::filter(`Month Published` > lubridate::ymd("2018-01-01"))  -->


<!-- plt = grouped_dockets |> -->
<!--   ggplot() + -->
<!--     geom_step(aes(x = `Month Published`, y = `Monthly Document Count`, color = Project)) + -->
<!--     theme_bw() + -->
<!--     labs( -->
<!--       title = "Advanced Reactor ADAMS Documents", -->
<!--       subtitle =  paste("as of", Sys.Date()) -->
<!--     ) + -->
<!--   scale_y_continuous( -->
<!--     breaks= seq(0, max(grouped_dockets$`Monthly Document Count`), by=20) -->
<!--     ) + -->
<!--   scale_x_date( -->
<!--     breaks= seq( -->
<!--       min(lubridate::ymd("2018-01-01")),  -->
<!--       max(grouped_dockets$`Month Published`),  -->
<!--       by = "year") -->
<!--     ) -->

<!-- plt |> plotly::ggplotly() -->
<!-- ``` -->


# Reports

This section is updated once a day and presents the Topical Reports, Technical Reports, Environmental Reports, and Safety Evaluations available on new reactor dockets. The last update was at `r Sys.time()`. The following dockets are searched: 

* `r nrcadams::docket_codex |> dplyr::pull(Project) |> paste(collapse = '\n * ')`

## Topical Reports

The following table summarizes tagged Topical Reports.


```{r}
Topicals = combined_dockets |>
  nrcadams::remove_noisy_files("Topical Report")

Topicals |>
  DT::datatable(
    caption = "Topical Reports",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Technical Paper

The following table summarizes tagged Technical Reports.


```{r}
Technicals = combined_dockets |>
  nrcadams::remove_noisy_files("Technical")

Technicals |>
  DT::datatable(
    caption = "Technical Paper",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Environmental Reports

The following table summarizes tagged Environmental Reports.

```{r}
Environmental = combined_dockets |>
  nrcadams::remove_noisy_files("Environmental")

Environmental |>
  DT::datatable(
    caption = "Environmental Reports",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Safety Analysis Reports

The following table summarizes tagged Safety Analysis Reports.

```{r}
Safety_Analysis = combined_dockets |>
  nrcadams::remove_noisy_files("Safety Analysis")

Safety_Analysis |>
  DT::datatable(
    caption = "Safety Analysis Documents",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```

## Safety Evaluations Reports

The following table summarizes tagged Safety Evaluations Reports.

```{r}
Safety_Evaluation = combined_dockets |>
  nrcadams::remove_noisy_files("Safety Evaluation")

Safety_Evaluation |>
  DT::datatable(
    caption = "Safety Evaluation Documents",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```
