---
title: "Docket Analytics and Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Docket Analytics and Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)
```


This page provides preliminary data analytics on various NLWR dockets. 
Note that ADAMS assigned multiple docket numbers to some reports.
The results presented here should be interpreted with these limitations.

# Pulling Advanced Reactor Docket Files

Because the entire docket is being pulled for each project, the 1,000 document
per search limit would be exceeded if all the dockets were pulled in one request. 
To reduce the impact of this limit, the `nrcadams::search_long_docket` is used 
to break the one long search into many smaller searches. 
This search was pre-conducted and the information prior to 2023 is exported by 
the `nrcadams::adv_reactor_dockets_lt_2023` variable. 
Dockets are individually search after 2023-01-01 and combined with the 
prior search information.

```{r}
combined_dockets = nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  purrr::map(~nrcadams::search_docket(.x, start_date = "2023-01-01")) |> 
  purrr::discard(\(z) nrow(z) == 0) |>
  purrr::reduce(dplyr::full_join) |>
  dplyr::full_join(nrcadams::adv_reactor_dockets_lt_2023) |>
  nrcadams::hyperlink_file_to_name() |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::select(-c(Company, DocketNumber)) |>
  dplyr::filter(!is.na(Project))

docket_count = combined_dockets |>
  dplyr::filter(NLWR) |>
  dplyr::select(-NLWR) |>
  dplyr::count(Project, sort = TRUE)

docket_count |>
  DT::datatable()
```

# Docket Plots

## Bar Plots

There are too many document types coded by ADAMS to effectively show on a plot 
(i.e., > 180).
As a result, the Type field is binned to facilitate a bar plot of various 
reactor applications. 
The last update to this plot was at `r Sys.time()`.

```{r}
library(ggplot2)
library(plotly)
docket_types = combined_dockets |>
  dplyr::filter(NLWR) |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
  ) |>
  nrcadams::simplify_type()

type_count = docket_types |>
  dplyr::filter(NLWR) |>
  dplyr::count(Type, sort = TRUE) |>
  dplyr::arrange(n)


plt = docket_types |>
  dplyr::mutate(Type = factor(Type, levels = type_count |> dplyr::pull(Type))) |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type)) +
    theme_bw() +
    scale_fill_brewer(palette="Set1") +
    labs(
      title = "Non-Light Water Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    xlab("Document Count")

plt |> ggplotly(tooltip = c("Type", "count"))
```

The same data can also be plotted with the bars unstacked.

```{r}
plt = docket_types |>
  dplyr::mutate(Type = factor(Type, levels = type_count |> dplyr::pull(Type))) |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type), position = position_dodge()) +
    theme_bw() +
    scale_fill_brewer(palette="Set1") +
    labs(
      title = "Non-Light Water Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    ) +
    xlab("Document Count")

plt |> ggplotly(tooltip = c("Type", "count"))
```

## Time Series

The cumulative number of documents on a given ADAMS docket is also presented
as a function of document date. 
The plot below shows the number of documents submitted to a docket. This 
plot starts in 2018 because the Shine docket singularly dominates the plot in 
the pre-2018 time frame. 
Plot order is sorted from highest number of documents, `r docket_count |> dplyr::filter(n == max(n)) |> dplyr::pull(Project)` 
to lowest number of documents, `r docket_count |> dplyr::filter(n == min(n)) |> dplyr::pull(Project)`.


```{r}
library(ggplot2)
library(plotly)
grouped_NLWR_dockets = combined_dockets |>
  dplyr::filter(NLWR) |>
  dplyr::group_by(Project) |>
  dplyr::arrange(`Publish Date`) |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
    count = 1,
    `Document Count` = cumsum(count)
    ) |>
  dplyr::filter(`Document Date` > lubridate::ymd("2018-01-01"))

plt = grouped_NLWR_dockets |>
  ggplot() +
    geom_step(aes(x = `Publish Date`, y = `Document Count`, color = Project)) +
    theme_bw() +
    labs(
      title = "Non-Light Water Reactor ADAMS Documents",
      subtitle =  paste("as of", Sys.Date())
    )
```

The data in linear scale:
```{r}
plt |> ggplotly()
```
The data in a y axis semi log scale:
```{r}
plt = plt + scale_y_log10() 
plt |> ggplotly()
```

# Reports

This section is updated once a day and presents the Topical Reports, Technical Reports, Environmental Reports, and Safety Evaluations available on new reactor dockets. The last update was at `r Sys.time()`. The following dockets are searched: 

* `r nrcadams::docket_codex |> dplyr::pull(Project) |> paste(collapse = '\n * ')`

## Topical Reports

The following table summarizes tagged Topical Reports.


```{r}
Topicals = combined_dockets |>
  nrcadams::remove_noisy_files("Topical Report")

Topicals |>
  DT::datatable(
    caption = "Topical Reports",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Technical Paper

The following table summarizes tagged Technical Reports.


```{r}
Technicals = combined_dockets |>
  nrcadams::remove_noisy_files("Technical")

Technicals |>
  DT::datatable(
    caption = "Technical Paper",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Environmental Reports

The following table summarizes tagged Environmental Reports.

```{r}
Environmental = combined_dockets |>
  nrcadams::remove_noisy_files("Environmental")

Environmental |>
  DT::datatable(
    caption = "Environmental Reports",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```


## Safety Analysis Reports

The following table summarizes tagged Safety Analysis Reports.

```{r}
Safety_Analysis = combined_dockets |>
  nrcadams::remove_noisy_files("Safety Analysis")

Safety_Analysis |>
  DT::datatable(
    caption = "Safety Analysis Documents",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```

## Safety Evaluations Reports

The following table summarizes tagged Safety Evaluations Reports.

```{r}
Safety_Evaluation = combined_dockets |>
  nrcadams::remove_noisy_files("Safety Evaluation")

Safety_Evaluation |>
  DT::datatable(
    caption = "Safety Evaluation Documents",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```
