---
title: "Docket Search"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Docket Search}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# What are Docket Numbers?

One of the more confusing aspects of the NRC's document repository how the NRC
assigns docket numbers. 
During pre-application engagement, the companies are assigned a docket number
that starts with `999`. 
Once the NRC accepts a companies license application for review, the NRC will
assign a docket number based upon the type of license. 
For example, companies applying for a traditional two stage license under 
Part 50 will have a docket number that begins with `050`.
Companies applying for a combined operating license under Part 52 will 
have a docket number that begins with `052`. 
Even after an applicant receives a docket number for a given facility or 
design, the applicant may still submit documents to the pre-application
docket if the information would support future licensing sumbitals. 

```{r}
nrcadams::docket_codex |>
  DT::datatable(
    caption = "Exported Docket Numbers in the `nrcadams` Package.",
    filter = list(position = 'top', clear = TRUE, plain = FALSE)
    )
```

# Keeping Up to Date with a Docket

As an open regulatory, the NRC is required to publicly provide non-proprietary
and non-export controlled information to the public.
When an applicant submits a proprietary document, the NRC will post the 
non-proprietary portions of the document on ADAMS. 
The NRC typically strives to ensure that enough information is in the public 
sphere to justify any licensing actions. 

To keep up-to-date with ACU's MSRR license, it is best to search through both
the pre-application and docketed information. 


```{r}
nrcadams::docket_codex |>
  dplyr::filter(Company == "ACU") |>
  dplyr::pull(Docket_Number) |>
  nrcadams::search_docket(days_back = 60) |>
  DT::datatable(
    caption = "The last 60 Days of the MSRR's Posted Licensing Documents.",
    filter = list(position = 'top', clear = TRUE, plain = FALSE)
    )
```

# Filtering a Docket for Actual Information

A given docket will include email correspondence in addition to reports and 
safety evaluations. 
Generally, letters and emails are more noise than signal and can be filtered
out of a search results.
Instead of mucking around with the ADAMS API to filter out these results,
it is simpler to use the `dplyr::filter` to filter on the returned results. 

```{r}
nrcadams::docket_codex |>
  dplyr::filter(Company == "X-Energy") |>
  dplyr::pull(Docket_Number) |>
  nrcadams::search_docket() |>
  dplyr::filter(
    !stringr::str_detect(Type, "E-Mail"),
    !stringr::str_detect(Type, "Letter")
    )|>
  DT::datatable(
    caption = "X-Energy's Pre-Applicaion Docket without Letters and Emails.",
    filter = list(position = 'top', clear = TRUE, plain = FALSE)
    )
```
