---
title: "Last Week in Dockets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Last Week in Dockets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

# Non-Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets:

* `r nrcadams::docket_codex |> dplyr::filter(NLWR) |> dplyr::pull(Project) |> cat(sep = "\n * ")`


```{r}
nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 7) |>
  dplyr::mutate(Title = paste0("<a href='", URL, "'>", Title, '</a>')) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(NLWR) |>
  dplyr::select(-c(URL, Company, DocketNumber, NLWR)) |>
  DT::datatable(
    caption = "The Last 7 Days of Posted NLWR Licensing Documents.",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```



# Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets:

* `r nrcadams::docket_codex |> dplyr::filter(!NLWR) |> dplyr::pull(Project) |> cat(sep = "\n * ")`


```{r}
nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 7) |>
  dplyr::mutate(Title = paste0("<a href='", URL, "'>", Title, '</a>')) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!NLWR) |>
  dplyr::select(-c(URL, Company, DocketNumber, NLWR)) |>
  DT::datatable(
    caption = "The Last 7 Days of Posted LWR Licensing Documents.",
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
```
