---
title: "Last Week in Dockets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Last Week in Dockets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The following page is updated once a day and presents the last week of posted ADAMS documents. The last update was at `r Sys.time()`.

```{r}
last_week_in_dockets = nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 7) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!is.na(Project))

build_html_table = function(docket_tbl, LWR) {
  if (LWR) {
    docket_tbl = docket_tbl |> 
      dplyr::filter(!NLWR)
    title = "The Last 7 Days of Posted LWR Licensing Documents."
  } else {
    docket_tbl = docket_tbl |> 
      dplyr::filter(NLWR)
    title = "The Last 7 Days of Posted NLWR Licensing Documents."
  }
    
  docket_tbl |> 
    dplyr::mutate(Title = paste0("<a href='", URL, "'>", Title, '</a>')) |>
    dplyr::select(-c(URL, Company, DocketNumber, NLWR)) |>
    DT::datatable(
      caption = title,
      filter = list(position = 'top', clear = TRUE, plain = FALSE),
      escape = FALSE
      )
}

docket_count = last_week_in_dockets |>
  dplyr::count(Project, sort = TRUE)

docket_count |>
  DT::datatable()

```

```{r}
library(ggplot2)
library(plotly)
plt = last_week_in_dockets |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project)),
    Type = dplyr::case_when(
      Type |> stringr::str_detect("RAI") ~ "RAI",
      Type |> stringr::str_detect("SAR") ~ "Safety Analysis",
      Type |> stringr::str_detect("Safety Analysis") ~ "Safety Analysis",
      Type |> stringr::str_detect("SER") ~ "Safety Eval.",
      Type |> stringr::str_detect("Safety Evaluation") ~ "Safety Eval.",
      Type |> stringr::str_detect("Audit") ~ "Audit",
      Type |> stringr::str_detect("Legal") ~ "Legal",
      Type |> stringr::str_detect("Letter") ~ "Letter",
      Type |> stringr::str_detect("E-Mail") ~ "Letter",
      Type |> stringr::str_detect("Report") ~ "Report",
      Type |> stringr::str_detect("Slides") ~ "Slides",
      Type |> stringr::str_detect("Public") ~ "Public",
      TRUE ~ "Other"
    )
  ) |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type)) +
    scale_fill_brewer(palette="Set1") +
    theme_bw() +
    labs(
      title = "New Advanced Reactor ADAMS Documents",
      subtitle =  paste("the week before", Sys.Date())
    ) +
    xlab("Document Count")

plt |> ggplotly(tooltip = c("count", "Type"))
```

# Non-Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets: 

* `r nrcadams::docket_codex |> dplyr::filter(NLWR) |> dplyr::pull(Project) |> paste(collapse = '\n * ')`


```{r}
last_week_in_dockets |> 
  build_html_table(LWR = FALSE)
```



# Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets:

* `r nrcadams::docket_codex |> dplyr::filter(!NLWR) |> dplyr::pull(Project) |> paste(collapse = '\n * ')`


```{r}
last_week_in_dockets |> 
  build_html_table(LWR = TRUE)
```
