---
title: "Last Week in Dockets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Last Week in Dockets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This page is updated Monday through Friday, hourly between 9AM ET and 5 PM ET. 
The last update was at `r Sys.time() |> lubridate::ymd_hms() |> lubridate::with_tz("America/New_York")` ET.

```{r}
last_week_in_dockets <- nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 7) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!is.na(Project))

build_html_table <- function(docket_tbl, LWR) {
  if (LWR) {
    docket_tbl = docket_tbl |>
      dplyr::filter(!NLWR)
    title = "The Last 7 Days of Posted LWR Licensing Documents."
  } else {
    docket_tbl = docket_tbl |>
      dplyr::filter(NLWR)
    title = "The Last 7 Days of Posted NLWR Licensing Documents."
  }
    
docket_tbl |> 
  nrcadams::hyperlink_file_to_name() |>
  dplyr::select(-c(Company, DocketNumber, NLWR)) |>
  DT::datatable(
    caption = title,
    filter = list(position = 'top', clear = TRUE, plain = FALSE),
    escape = FALSE
    )
}

docket_count = last_week_in_dockets |>
  dplyr::count(Project, sort = TRUE)

docket_count |>
  DT::datatable()

```

```{r}
library(ggplot2)
library(plotly)
plt = last_week_in_dockets |>
  dplyr::mutate(
    Project = factor(Project, levels = docket_count |> dplyr::pull(Project))
  ) |> 
  nrcadams::simplify_type() |>
  ggplot() +
    geom_bar(aes(y = Project, fill = Type)) +
    scale_fill_brewer(palette="Set1") +
    theme_bw() +
    labs(
      title = "New Advanced Reactor ADAMS Documents",
      subtitle =  paste("the week before", Sys.Date())
    ) +
    xlab("Document Count")

plt |> ggplotly(tooltip = c("count", "Type"))
```

# Non-Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets: 

* `r nrcadams::docket_codex |> dplyr::filter(NLWR) |> dplyr::pull(Project) |> paste(collapse = '\n * ')`


```{r}
last_week_in_dockets |> 
  build_html_table(LWR = FALSE)
```



# Light Water Reactor Docket Search

The following table summarizes all ADAMS documents for the following dockets:

* `r nrcadams::docket_codex |> dplyr::filter(!NLWR) |> dplyr::pull(Project) |> paste(collapse = '\n * ')`


```{r}
last_week_in_dockets |> 
  build_html_table(LWR = TRUE)
```


