---
title: "RSS Files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RSS Files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
here::here("docs", "RSS") |> dir.create(recursive = TRUE)

```


This page is updated Monday through Friday, hourly between 9AM ET and 5 PM ET. 
It presents RSS files for the various dockets tracked by the `nrcadams` package. 
The last update was at `r Sys.time() |> lubridate::ymd_hms() |> lubridate::with_tz("America/New_York")` ET.

# Using the RSS Feeds

If you are unfamiliar with RSS readers, they are magical. 
Here is an article that can point you to some of the best. 
I generally just use the slack feed reader which is cool 
because it can enable easy conversations within our team about key documents.

https://www.theverge.com/24036427/rss-feed-reader-best

# Making RSS files

The following code shows the user how they can generate RSS files to help keep updated 
with their favorite ADAMS search results.


# Advanced Reactor Dockets

The RSS files generated on this page and updated by this site are located at
the URLs shown in the table below.

```{r adv-reactor-RSS}
last_week_in_dockets = nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 14) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!is.na(Project))


nrcadams::docket_codex |>
  dplyr::pull(Project) |>
  purrr::walk(\(.x) {
    last_week_in_dockets |>
      dplyr::filter(Project == .x) |>
      nrcadams::write_rss(
        file = here::here("docs", "RSS", paste0(
          .x |> stringr::str_replace_all(" ", "_"), ".rss")
          ),
        title = .x 
        )
  })
  
last_week_in_dockets |> 
  nrcadams::write_rss(file = here::here("docs", "RSS", "dockets.rss")) 


nrcadams::docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(
    `RSS File` = paste0(
      "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
      Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```

# Research and Test Reactors

And if you are more interested in tracking RTRs (no reason in particular), these RSS files might help.

```{r}
last_week_in_RTRs <- nrcadams::RTR_docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 14)

if (length(last_week_in_RTRs) != 0) {
  last_week_in_RTRs <- last_week_in_RTRs |>
    dplyr::left_join(nrcadams::RTR_docket_codex) |>
    dplyr::filter(!is.na(Project))

  nrcadams::RTR_docket_codex |>
    dplyr::pull(Project) |>
    purrr::walk(\(.x) {
      last_week_in_RTRs |>
        dplyr::filter(Project == .x) |>
        nrcadams::write_rss(
          file = here::here("docs", "RSS", paste0(
            .x |> stringr::str_replace_all(" ", "_"), ".rss")
            ),
          title = .x 
          )
    })
}

nrcadams::RTR_docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets-RTR.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```

# ACRS

```{r}
ACRS <- nrcadams::search_values(
  days_back = 30,
  author_affiliation = "NRC/ACRS",
  results_tag = "ACRS"
  )

if (length(ACRS) != 0) {
  ACRS |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", paste0(
        "ACRS", ".rss")
      ),
      title = "ACRS"
    )
}

tibble::tibble(Project = "ACRS") |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project,
    ".rss"
  )) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```


# Undocketed Company Mentions (Experimental)

Do you want to know who else is talking about a company outside of a docket? 
This list of RSS files searches for a company name that is not also tagged with a
docket number associated with that company. 


```{r, burning-ears-table}

toobigtotrack <- c("Holtec", "GE", "Westinghouse")

date <- nrcadams:::process_dates(days_back = 14)

burning_ears <- nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::pull(Company) |>
  purrr::map_dfr(\(.x) {
    antidocket <- nrcadams::docket_codex |>
      dplyr::filter(Company  == .x) |>
      dplyr::mutate(DocketNumber = -DocketNumber) |>
      dplyr::pull(DocketNumber)

    nrcadams::search_public_ADAMS(
      search_term = .x,
      DocketNumber = antidocket,
      start_date = date$start,
      results_tag = .x
    )
  })

nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::pull(Company) |>
  purrr::walk(\(.x) {
    burning_ears |>
      dplyr::filter(tag == .x) |>
      nrcadams::write_rss(
        file = here::here("docs", "RSS", paste0(
          .x |>
            stringr::str_replace_all(" ", "_") |>
            stringr::str_replace_all("/", "_"),
          ".rss"
        )),
        title = .x
      )
  })


nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Company |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  nrcadams::hyperlink_file_to_name(
    name_vct = `RSS File`,
    url_vct = `RSS File`
  )|>
  DT::datatable(escape = FALSE)
```

# NRC Source Term Codes

```{r extra-searches, echo = FALSE, results=FALSE}
code_search <- tibble::tibble(
  tag = c(
    "MELCOR", "ARCON", "RADTRAD", "NRCDose3",
    "MACCS", "Sierra ATD", "GOTHIC"
  )
) |>
  dplyr::mutate(
    search = dplyr::case_when(
      tag == "Sierra ATD" ~ "'%22SIERRA+ATD%22'",
      .default = tag
    )
  )

code_results <- code_search |>
  purrr::pmap(\(tag = tag, search = search) {
    nrcadams::search_values(
      search_term = search,
      results_tag = tag,
      days_back = 7
    )
  }) |>
  # Need to remove empty search results
  purrr::discard(\(z) nrow(z) == 0)

if(!length(code_results) == 0) {
  code_results <- code_results |>
    purrr::reduce(dplyr::full_join)

  code_search |>
    dplyr::pull(tag) |>
    purrr::walk(\(.x) {
      code_results |>
        dplyr::filter(tag == .x) |>
        nrcadams::write_rss(
          file = here::here("docs", "RSS", paste0(
            .x |> stringr::str_replace_all(" ", "_"), ".rss")
          ),
          title = .x
        )
    })

  code_results |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", "SourceTermCodes.rss"),
      title = "Source Term Code Reports"
    )
}

# Search for Documents

document_search <- tibble::tibble(
  tag = c("NEI 22-04")
) |>
  dplyr::mutate(
    search = dplyr::case_when(
      tag == "NEI 22-04" ~ "'NEI+22-04'",
      .default = tag
    ) 
  )

document_results <- document_search |>
  purrr::pmap(\(tag = tag, search = search) {
    nrcadams::search_values(
      search_term = search,
      results_tag = tag,
      days_back = 30
    )
  }) |>
  # Need to remove empty search results
  purrr::discard(\(z) nrow(z) == 0)

if(!length(document_results) == 0) {
  document_results <- document_results |>
    purrr::reduce(dplyr::full_join)

  document_search |>
    dplyr::pull(tag) |>
    purrr::walk(\(.x) {
      document_results |>
        dplyr::filter(tag == .x) |>
        nrcadams::write_rss(
          file = here::here("docs", "RSS", paste0(
            .x |> stringr::str_replace_all(" ", "_"), ".rss"
          )),
          title = .x
        )
    })
}




# Inspections <- nrcadams::search_values(
#     document_type = "Inspection Manual",
#     author_affiliation = "NRC/NRR",
#     results_tag = "Inspections",
#     days_back = 7
# )

# if (length(Inspections) != 0) {
#   Inspections |>
#     nrcadams::write_rss(
#       file = here::here("docs", "RSS", paste0(
#         "Inspections", ".rss")
#         ),
#       title = "Inspections"
#       )
# }

KP_meetings <- last_week_in_dockets |>
  dplyr::filter(
    Company == "Kairos Power",
    stringr::str_detect(Type, "Meeting Agenda")
  )

if (length(KP_meetings) != 0) {
  KP_meetings |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", paste0(
        "kp_meetings", ".rss")
      ),
      title = "Kairos Power Meetings"
    )
}

```


```{r}
code_search |>
  dplyr::mutate(
    `RSS File` = paste0(
      "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
      tag |> stringr::str_replace_all(" ", "_"),
      ".rss"
    )
  ) |>
  dplyr::add_row(
    tag = "All Codes",
    search = "Or Gate",
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/SourceTermCodes.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`) |>
  DT::datatable(escape = FALSE)
```
