 ---
title: "RSS Files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RSS Files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This page is updated Monday through Friday, hourly between 9AM ET and 5 PM ET. 
It presents RSS files for the various dockets tracked by the `nrcadams` package. 
The last update was at `r Sys.time() |> lubridate::ymd_hms() |> lubridate::with_tz("America/New_York")` ET.

`These RSS files are still under testing and development. Use at your own risk.`

# Making RSS files

The following code shows the user how they can generate RSS files to help keep updated with their favorite ADAMS search results.

```{r}
last_week_in_dockets = nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 7) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!is.na(Project))

here::here("docs", "RSS") |> dir.create(recursive = TRUE)

nrcadams::docket_codex |>
  dplyr::pull(Project) |>
  purrr::walk(\(.x) {
    last_week_in_dockets |>
      dplyr::filter(Project == .x) |>
      nrcadams::write_rss(
        file = here::here("docs", "RSS", paste0(
          .x |> stringr::str_replace_all(" ", "_"), ".rss")
          ),
        title = .x 
        )
  })
  
last_week_in_dockets |> nrcadams::write_rss(file = here::here("docs", "RSS", "dockets.rss")) 
```

# Locations of Locally Supported RSS Files

The RSS files generated on this page and updated by this site are located at
the URLs shown in the table below.

```{r}
nrcadams::docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```

# Research and Test Reactors

And if you are more interested in tracking RTRs (no reason in particular), these RSS files might help.

```{r}
nrcadams::RTR_docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```
