---
title: "RSS Files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RSS Files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This page is updated Monday through Friday, hourly between 9AM ET and 5 PM ET. 
It presents RSS files for the various dockets tracked by the `nrcadams` package. 
The last update was at `r Sys.time() |> lubridate::ymd_hms() |> lubridate::with_tz("America/New_York")` ET.

`These RSS files are still under testing and development. Use at your own risk.`

# Making RSS files

The following code shows the user how they can generate RSS files to help keep updated with their favorite ADAMS search results.

```{r}
here::here("docs", "RSS") |> dir.create(recursive = TRUE)


last_week_in_dockets = nrcadams::docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 14) |>
  dplyr::left_join(nrcadams::docket_codex) |>
  dplyr::filter(!is.na(Project))


nrcadams::docket_codex |>
  dplyr::pull(Project) |>
  purrr::walk(\(.x) {
    last_week_in_dockets |>
      dplyr::filter(Project == .x) |>
      nrcadams::write_rss(
        file = here::here("docs", "RSS", paste0(
          .x |> stringr::str_replace_all(" ", "_"), ".rss")
          ),
        title = .x 
        )
  })
  
last_week_in_dockets |> nrcadams::write_rss(file = here::here("docs", "RSS", "dockets.rss")) 


last_week_in_RTRs <- nrcadams::RTR_docket_codex |>
  dplyr::pull(DocketNumber) |>
  nrcadams::search_docket(days_back = 14)

if (length(last_week_in_RTRs) != 0) {
  last_week_in_RTRs <- last_week_in_RTRs |>
    dplyr::left_join(nrcadams::RTR_docket_codex) |>
    dplyr::filter(!is.na(Project))
    
  nrcadams::RTR_docket_codex |>
    dplyr::pull(Project) |>
    purrr::walk(\(.x) {
      last_week_in_RTRs |>
        dplyr::filter(Project == .x) |>
        nrcadams::write_rss(
          file = here::here("docs", "RSS", paste0(
            .x |> stringr::str_replace_all(" ", "_"), ".rss")
            ),
          title = .x 
          )
    })
}

ACRS <- nrcadams::search_ACRS(days_back = 14)

if (length(ACRS) != 0) {
  ACRS |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", paste0(
        "ACRS", ".rss")
        ),
      title = "ACRS"
      )  
}

# Undocketed

toobigtotrack <- c("Holtec", "GE", "Westinghouse")

burning_ears = nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::pull(Company) |>
  purrr::map_dfr(\(.x) {
    nrcadams::search_undocketed(.x, days_back = 14) 
    }
  )

nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::pull(Company) |>
  purrr::walk(\(.x) {
    burning_ears |>
      dplyr::filter(Tag == .x) |>
      nrcadams::write_rss(
        file = here::here("docs", "RSS", paste0(
          .x |> stringr::str_replace_all(" ", "_")|> stringr::str_replace_all("/", "_"), ".rss")
          ),
        title = .x 
        )
  })


```

# Locations of Locally Supported RSS Files

The RSS files generated on this page and updated by this site are located at
the URLs shown in the table below.

```{r}
nrcadams::docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```

# Research and Test Reactors

And if you are more interested in tracking RTRs (no reason in particular), these RSS files might help.

```{r}
nrcadams::RTR_docket_codex |>
  dplyr::select(Project) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project |> stringr::str_replace_all(" ", "_"),
    ".rss"
  )) |>
  dplyr::add_row(
    Project = "All Dockets", 
    `RSS File` = "https://mrdenman-nuclear.github.io/nrcadams/RSS/dockets-RTR.rss"
    ) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```

# ACRS

```{r}
tibble::tibble(Project = "ACRS") |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Project,
    ".rss"
  )) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)

```


# Undocketed Company Mentions (Experimental)

Do you want to know who else is talking about a compnay outside of a docket? 
This list of RSS files searches for a company name that is not also tagged with a
docket number associated with that company. 


```{r}
nrcadams::docket_codex |>
  dplyr::filter(!Company %in% toobigtotrack) |>
  dplyr::distinct(Company) |>
  dplyr::mutate(`RSS File` = paste0(
    "https://mrdenman-nuclear.github.io/nrcadams/RSS/",
    Company,
    ".rss"
  )) |>
  nrcadams::hyperlink_file_to_name(name_vct = `RSS File`, url_vct = `RSS File`)|>
  DT::datatable(escape = FALSE)
```



```{r, echo = FALSE}
inpsection <- nrcadams::search_advanced(
    search_field = "properties_search_all:!(!(DocumentType,eq,%27Inspection+Manual%27,%27%27),!(AuthorAffiliation,starts,NRC/NRR,%27%27),",
    results_tag = "Inspections",
    days_back = 15
)


  inpsection |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", paste0(
        "inpsection", ".rss")
        ),
      title = "Inpsection"
      )  

KP_meetings <- last_week_in_dockets |> 
  dplyr::filter(
    Company == "Kairos Power",
    stringr::str_detect(Type, "Meeting Agenda")
    ) 
    
    

if (length(KP_meetings) != 0) {
  KP_meetings |>
    nrcadams::write_rss(
      file = here::here("docs", "RSS", paste0(
        "kp_meetings", ".rss")
        ),
      title = "Kairos Power Meetings"
      )  
}

```